Recurrent Neural Networks

### 2017-08-28 deeplearn/presentation/paper_2.tex
Text Generator bug fix

We describe a more general situation. Let $S$ be a (finite) set of {\em states} with a distinguished element $\perp\in S$, and consider a function $f:A\times S\to B\times S$. Let $a_1,...,a_n$ be a finite sequence of elements of $A$.  We define two sequences $b_1,...,b_n$ and $s_1,...,s_n$ of elements of $B$ and $S$ respectively as follows.  We first define $b_1, s_1 = f(a_1, \perp)$.  Suppose that we have defined the elements $b_1,...,b_n$ and $s_1,...,s_n$.  We define $b_{n+1}$ and $s_{n+1}$ via $b_{n+1}, s_{n+1} = f(a_{n+1}, s_n)$.  We define $f^*(a_1...a_n)=b_1...b_n$, with $b_1,...,b_n$ defined as above.  This is a function $f^*:A^*\to B^*$, and it has the property that the length of the output sequence is the same as that of the input sequence.  An interesting special case of this is when $S=B$. In this case, we can have $f:A\times B\to B$. We can define b_1 = f(a_1, \perp)$, and $b_{n+1}=f(a_{n+1}, b_n)$. This is in fact the main type of function we use in our examples later. Note that this is a state machine, close to a deterministic finite automaton, except that here the state space $S$ is allowed to be infinite.

@@

%(GRAPHICAL REPRESENTATION OF NETWORK)
\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=1cm]
    \tikzstyle{arrow} = [thick,->,>=stealth]
    \tikzstyle{startstop} = [rectangle, minimum width=1.5cm, minimum height=.6cm, text centered, draw=black, fill=black!20]
    \node (input) [] at (0cm,1cm) {};
    \node (output) [] at (0cm,-3cm) {};
    \node (s-input-A) [] at (-2cm,0cm) {};
    \node (s-output-A) [] at (10cm,0cm) {};
    \node (s-input-B) [] at (-2cm,-1cm) {};
    \node (s-output-B) [] at (10cm,-1cm) {};
    \node (s-input-C) [] at (-2cm,-2cm) {};
    \node (s-output-C) [] at (10cm,-2cm) {};
    \path[] node[startstop] (A-0) at (0cm,0cm) {};
    \path[] node[startstop] (B-0) at (0cm,-1cm) {};
    \path[] node[startstop] (C-0) at (0cm,-2cm) {};
    \draw [arrow] (input) -- (A);
    \draw [arrow] (s-input-A) -- (A-0);
    \draw [arrow] (s-input-B) -- (B-0);
    \draw [arrow] (s-input-C) -- (C-0);
    \draw [arrow] (A) -- (B);
    \draw [arrow] (B) -- (C);
    \draw [arrow] (C) -- (output);

\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=1cm]
    \tikzstyle{every pin edge}=[<-,shorten <=1pt]
    \tikzstyle{neuron}=[circle,fill=black!50,minimum size=10pt,inner sep=0pt]

    % Draw the hidden layer nodes
    \foreach \name / \x in {1,...,5}
        \path[yshift=0.5cm]
            node[neuron] (I-\name) at (\x,-0cm) {};

    \foreach \name / \x in {1,...,5}
        \path[yshift=0.5cm]
            node[neuron] (H-\name) at (\x,-2cm) {};

    \foreach \source in {1,...,5}
        \foreach \dest in {1,...,5}
            \path (I-\source) edge (H-\dest);

    \foreach \name / \x in {1,...,5}
        \path[yshift=0.5cm]
            node[neuron] (K-\name) at (\x,-4 cm) {};

    \foreach \source in {1,...,5}
        \foreach \dest in {1,...,5}
            \path (H-\source) edge (K-\dest);
\end{tikzpicture}

The base input ofor this network is a (unicode) character, which is one-hot encoded before being fed into the
 recurrent layers.  For training, the network is unrolled to a length of 256 characters,
 which is about twice the length  of an average message in our database, and all strings are padded or truncated
 to a length of 256 characters.

@@

\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=1cm]
    \tikzstyle{arrow} = [thick,->,>=stealth]
    \tikzstyle{startstop} = [rectangle, minimum width=1.5cm, minimum height=.6cm, text centered, draw=black, fill=black!20]
    \node (input) [] at (0cm,1cm) {};
    \node (output) [] at (0cm,-3cm) {};
    \node (s-input-A) [] at (-2cm,0cm) {};
    \node (s-output-A) [] at (10cm,0cm) {};
    \node (s-input-B) [] at (-2cm,-1cm) {};
    \node (s-output-B) [] at (10cm,-1cm) {};
    \node (s-input-C) [] at (-2cm,-2cm) {};
    \node (s-output-C) [] at (10cm,-2cm) {};
    \path[] node[startstop] (A-0) at (0cm,0cm) {};
    \path[] node[startstop] (B-0) at (0cm,-1cm) {};
    \path[] node[startstop] (C-0) at (0cm,-2cm) {};
    \draw [arrow] (input) -- (A);
    \draw [arrow] (s-input-A) -- (A-0);
    \draw [arrow] (s-input-B) -- (B-0);
    \draw [arrow] (s-input-C) -- (C-0);
    \draw [arrow] (A) -- (B);
    \draw [arrow] (B) -- (C);
    \draw [arrow] (C) -- (output);

@@

\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=1cm]
    \tikzstyle{arrow} = [thick,->,>=stealth]
    \tikzstyle{startstop} = [rectangle, minimum width=1.5cm, minimum height=.6cm, text centered, draw=black, fill=black!20]
    \node (input) [] at (0cm,1cm) {};
    \node (output) [] at (0cm,-3cm) {};
    \node (s-input-A) [] at (-2cm,0cm) {};
    \node (s-output-A) [] at (10cm,0cm) {};
    \node (s-input-B) [] at (-2cm,-1cm) {};
    \node (s-output-B) [] at (10cm,-1cm) {};
    \node (s-input-C) [] at (-2cm,-2cm) {};
    \node (s-output-C) [] at (10cm,-2cm) {};
    \path[] node[startstop] (A-0) at (0cm,0cm) {};
    \path[] node[startstop] (B-0) at (0cm,-1cm) {};
    \path[] node[startstop] (C-0) at (0cm,-2cm) {};
    \draw [arrow] (input) -- (A);
    \draw [arrow] (s-input-A) -- (A-0);
    \draw [arrow] (s-input-B) -- (B-0);
    \draw [arrow] (s-input-C) -- (C-0);
    \draw [arrow] (A) -- (B);
    \draw [arrow] (B) -- (C);
    \draw [arrow] (C) -- (output);

>>>>

We describe a more general situation. Let $S$ be a (finite) set of {\em states} with a distinguished element $\perp\in S$, and consider a function $f:A\times S\to B\times S$. Let $a_1,...,a_n$ be a finite sequence of elements of $A$.  We define two sequences $b_1,...,b_n$ and $s_1,...,s_n$ of elements of $B$ and $S$ respectively as follows.  We first define $b_1, s_1 = f(a_1, \perp)$.  Suppose that we have defined the elements $b_1,...,b_n$ and $s_1,...,s_n$.  We define $b_{n+1}$ and $s_{n+1}$ via $b_{n+1}, s_{n+1} = f(a_{n+1}, s_n)$.  We define $f^*(a_1...a_n)=b_1...b_n$, with $b_1,...,b_n$ defined as above.  This is a function $f^*:A^*\to B^*$, and it has the property that the length of the output sequence is the same as that of the input sequence.  An interesting special case of this is when $S=B$. In this case, we can have $f:A\times B\to B$. We can define $b_1 = f(a_1, \perp)$, and $b_{n+1}=f(a_{n+1}, b_n)$. This is in fact the main type of function we use in our examples later. Note that this is a state machine, close to a deterministic finite automaton, except that here the state space $S$ is allowed to be infinite.

@@

%(GRAPHICAL REPRESENTATION OF NETWORK)
\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=1cm]
    \tikzstyle{arrow} = [thick,->,>=stealth]
     \tikzstyle{every pin edge}=[<-,shorten <=1pt]
     \tikzstyle{neuron}=[circle,fill=black!50,minimum size=6pt,inner sep=0pt]

    \tikzstyle{startstop} = [rectangle, minimum width=1.5cm, minimum height=.6cm, text centered, draw=black, fill=black!20]
    \node (input) [] at (0cm,1cm) {};
    \node (output) [] at (0cm,-2.25cm) {};
    \node (s-input-A) [] at (-2cm,0cm) {};
    \node (s-output-A) [] at (10cm,0cm) {};
    \node (s-input-B) [] at (-2cm,-1cm) {};
    \node (s-output-B) [] at (10cm,-1cm) {};
    \node (s-input-C) [] at (-2cm,-2cm) {};
    \node (s-output-C) [] at (10cm,-2cm) {};
    \path[] node[startstop] (A-0) at (0cm,0cm) {};
    \path[] node[startstop] (B-0) at (0cm,-1cm) {};
    \path[] node[startstop] (C-0) at (0cm,-2cm) {};
    \draw [arrow] (input) -- (A);
    \draw [arrow] (s-input-A) -- (A-0);
    \draw [arrow] (s-input-B) -- (B-0);
    \draw [arrow] (s-input-C) -- (C-0);
    \draw [arrow] (A) -- (B);
    \draw [arrow] (B) -- (C);
    %\draw [arrow] (C) -- (output);

     \foreach \i/\j in {1/0,2/1,3/2,4/3}
     {
       \node (input-\i) [] at (2*\i cm,1cm) {};
       \node (output-\i) [] at (2*\i cm,-2.25cm) {};
       \path[] node[startstop] (A-\i) at (2*\i cm,0cm) {};
       \path[] node[startstop] (B-\i) at (2*\i cm,-1cm) {};
       \path[] node[startstop] (C-\i) at (2*\i cm,-2cm) {};
       \draw [arrow] (A-\i) -- (B-\i);
       \draw [arrow] (B-\i) -- (C-\i);
       \draw [arrow] (input-\i) -- (A-\i);
       \draw [arrow] (A-\j) -- (A-\i);
       \draw [arrow] (B-\j) -- (B-\i);
       \draw [arrow] (C-\j) -- (C-\i);
       %5\draw [arrow] (C-\i) -- (output-\i);
     }
     \draw [arrow] (A-4) -- (s-output-A);
     \draw [arrow] (B-4) -- (s-output-B);
     \draw [arrow] (C-4) -- (s-output-C);

     \foreach \name / \x in {1,...,15} {
         \path[xshift=-1cm]
             node[neuron] (I-\name) at (0.3*\x,-3.5cm) {};
             \path (output) edge (I-\name);
             }

     \foreach \name / \x in {1,...,15} {
         \path[xshift=4.5cm]
             node[neuron] (J-\name) at (0.3*\x,-3.5cm) {};
            \path (output-4) edge (J-\name); }

     \foreach \name / \x in {1,...,15}{
         \path[xshift=1.5cm]
             node[neuron] (K-\name) at (0.3*\x,-4.5cm) {};
        \path (I-\name) edge (K-\name);
        \path (J-\name) edge (K-\name); }

        \foreach \name / \x in {1,...,4}{
            \path[xshift=3cm] node[neuron] (O-\name) at (0.3*\x,-5.25cm) {};
            \foreach \j in {1,...,15}{
           \path (K-\j) edge (O-\name);}
           %\path (J-\name) edge (K-\name);
           }

%     \foreach \name / \x in {1,...,5}
%         \path[yshift=0.5cm]
%             node[neuron] (H-\name) at (\x,-2cm) {};

%\end{tikzpicture}
%
%
%\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=1cm]
    %
    % % Draw the hidden layer nodes
    %
    % \foreach \source in {1,...,5}
    %     \foreach \dest in {1,...,5}
    %         \path (I-\source) edge (H-\dest);
    %
    % \foreach \name / \x in {1,...,5}
    %     \path[yshift=0.5cm]
    %         node[neuron] (K-\name) at (\x,-4 cm) {};
    %
    % \foreach \source in {1,...,5}
    %     \foreach \dest in {1,...,5}
    %         \path (H-\source) edge (K-\dest);
\end{tikzpicture}

The base input for this network is a (unicode) character, which is one-hot encoded before being fed into the
 recurrent layers.  For training, the network is unrolled to a length of 256 characters,
 which is about twice the length  of an average message in our database, and all strings are padded or truncated
 to a length of 256 characters.

@@

\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=1cm]
    \tikzstyle{arrow} = [thick,->,>=stealth]
    \tikzstyle{startstop} = [rectangle, minimum width=1.5cm, minimum height=.6cm, text centered, draw=black, fill=black!20]
    \tikzstyle{neuron}=[circle,fill=black!50,minimum size=6pt,inner sep=0pt]

    \node (input) [] at (0cm,1cm) {};
    \node (output) [] at (0cm,-3cm) {};
    \node (s-input-A) [] at (-2cm,0cm) {};
    \node (s-output-A) [] at (10cm,0cm) {};
    \node (s-input-B) [] at (-2cm,-1cm) {};
    \node (s-output-B) [] at (10cm,-1cm) {};
    \node (s-input-C) [] at (-2cm,-2cm) {};
    \node (s-output-C) [] at (10cm,-2cm) {};
    \path[] node[startstop] (A-0) at (0cm,0cm) {};
    \path[] node[startstop] (B-0) at (0cm,-1cm) {};
    \path[] node[startstop] (C-0) at (0cm,-2cm) {};
    \draw [arrow] (input) -- (A);
    \draw [arrow] (s-input-A) -- (A-0);
    \draw [arrow] (s-input-B) -- (B-0);
    \draw [arrow] (s-input-C) -- (C-0);
    \draw [arrow] (A) -- (B);
    \draw [arrow] (B) -- (C);
    \draw [arrow] (C) -- (output);

     \foreach \i/\j in {1/0,2/1,3/2,4/3}
     {
       \node (input-\i) [] at (2*\i cm,1cm) {};
       \node (output-\i) [] at (2*\i cm,-2.25cm) {};
       \path[] node[startstop] (A-\i) at (2*\i cm,0cm) {};
       \path[] node[startstop] (B-\i) at (2*\i cm,-1cm) {};
       \path[] node[startstop] (C-\i) at (2*\i cm,-2cm) {};
       \draw [arrow] (A-\i) -- (B-\i);
       \draw [arrow] (B-\i) -- (C-\i);
       \draw [arrow] (input-\i) -- (A-\i);
       \draw [arrow] (A-\j) -- (A-\i);
       \draw [arrow] (B-\j) -- (B-\i);
       \draw [arrow] (C-\j) -- (C-\i);
       \draw [arrow] (C-\i) -- (output-\i);
     }
     \draw [arrow] (A-4) -- (s-output-A);
     \draw [arrow] (B-4) -- (s-output-B);
     \draw [arrow] (C-4) -- (s-output-C);

     \foreach \name / \x in {1,...,15}{
         \path[xshift=0cm]
             node[neuron] (K-\name) at (0.5*\x,-3.5cm) {};
        \path (output-2) edge (K-\name);
        %\path (J-\name) edge (K-\name);
        }

        \foreach \name / \x in {1,...,10}{
            \path[xshift=1cm] node[neuron] (O-\name) at (0.6*\x,-5.75cm) {};
            \foreach \j in {1,...,15}{
           \path (K-\j) edge (O-\name);}
           %\path (J-\name) edge (K-\name);
           }

@@

\begin{tikzpicture}[shorten >=1pt,->,draw=black!50, node distance=1cm]
    \tikzstyle{arrow} = [thick,->,>=stealth]
    \tikzstyle{startstop} = [rectangle, minimum width=1.5cm, minimum height=.6cm, text centered, draw=black, fill=black!20]
    \node (input) [] at (0cm,1cm) {};
    \node (output) [] at (0cm,-3cm) {};
    \node (s-input-A) [] at (-2cm,0cm) {};
    \node (s-output-A) [] at (10cm,0cm) {};
    \node (s-input-B) [] at (-2cm,-1cm) {};
    \node (s-output-B) [] at (10cm,-1cm) {};
    \node (s-input-C) [] at (-2cm,-2cm) {};
    \node (s-output-C) [] at (10cm,-2cm) {};
    \path[] node[startstop] (A-0) at (0cm,0cm) {};
    \path[] node[startstop] (B-0) at (0cm,-1cm) {};
    \path[] node[startstop] (C-0) at (0cm,-2cm) {};
    \draw [arrow] (input) -- (A);
    \draw [arrow] (s-input-A) -- (A-0);
    \draw [arrow] (s-input-B) -- (B-0);
    \draw [arrow] (s-input-C) -- (C-0);
    \draw [arrow] (A-0) -- (B-0);
    \draw [arrow] (B-0) -- (C-0);
    \draw [arrow] (C-0) -- (output);
